---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r chunk1, echo=TRUE}
dact <- read.csv(unz("./activity.zip", "activity.csv"))
as.Date(dact$date, format="%Y-%m-%d")

´´´  

## What is mean total number of steps taken per day?
```{r cunk2, echo=TRUE}
sv <- split(dact$steps, dact$date)
vv <- lapply(sv, function(x) sum(x, na.rm = TRUE))
v  <- as.numeric(vv[!is.na(vv)])
hist(v, col="red", breaks=seq(from=0, to=25000, by=2500), xlab="Total number of steps per day", ylab="Frequency", main="Histogram of the total number of steps taken each day")
dev.copy(png, file="plot1.png", height=480, width=480)
dev.off()
meanv    <- round(mean(v))
medianv  <- median(v)
cat("Mean   = ", meanv)
cat("Median = ", medianv)
´´´
## What is the average daily activity pattern?
```{r cunk3, echo=TRUE}
sp <- split(dact$steps, dact$interval)
vms <- sapply(sp, function(x) mean(x, na.rm = TRUE))
plot(x=as.numeric(names(vms)),y=vms, type="l", xlab="Time/Five-minute interval", ylab="Average number of steps", col="blue")
dev.copy(png, file="plot2.png", height=480, width=480)
dev.off()
#barplot(height = vms, xlab="Time/Five-minute interval", ylab="Average number of steps", col="blue")
cat("Maximum value =", max(vms))
cat("Indx Maximum value =")
which.max(vms)

## Imputing missing values
nna <- sum(is.na(dact$steps))
cat("Number of missing values =", nna)
fact <- dact
pos_na <- which(is.na(fact$steps))
vec_m  <- rep(mean(fact$steps, na.rm = TRUE), times=length(pos_na))
fact[pos_na, 1] = vec_m
rm(vec_m, pos_na)

vk   <- as.numeric(lapply(split(fact$steps, fact$date), function(x) sum(x)))
hist(vk, col="red", breaks=seq(from=0, to=25000, by=2500), xlab="Total number of steps per day", ylab="Frequency", main="Histogram of the total number of steps taken each day")
dev.copy(png, file="plot3.png", height=480, width=480)
dev.off() 
meanvk    <- round(mean(vk))
medianvk  <- median(vk)
cat("Mean   = ", meanvk)
cat("Median = ", round(medianvk))


## Are there differences in activity patterns between weekdays and weekends?
library(timeDate)
fact["TypeDay"] <- factor(isWeekday(fact$date), levels=c(TRUE,FALSE), labels=c("weekday", "weekend"))
fact["WeekDay"] <- weekdays(as.Date(fact$date))
mean_fact <- aggregate(fact$steps, by=list(fact$TypeDay,fact$WeekDay, fact$interval), mean)
names(mean_fact) <- c("TypeDay", "WeekDay", "interval","mean_steps")
library(lattice)
xyplot(mean_fact$mean ~ mean_fact$interval | mean_fact$TypeDay, 
       type="l", 
       lwd=1, 
       xlab="Interval", 
       ylab="Number of steps", 
       layout=c(1,2))
dev.copy(png, file="plot4.png", height=480, width=480)
dev.off() 
#vwkd <- fact[fact$TypeDay=="weekday",]
#vwkn <- fact[fact$TypeDay=="weekend",]
#svwkd <- lapply(split(vwkd$steps, vwkd$interval), function(x) mean(x))
#svwkn <- lapply(split(vwkn$steps, vwkn$interval), function(x) mean(x))
#plot(x=as.numeric(names(svwkd)),y=svwkd, type="l", xlab="Time/Five-minute interval", ylab="Average number of steps", col="blue")
#lines(x=as.numeric(names(svwkn)), y=svwkn, col="red")
#dev.copy(png, file="plot4.png", height=480, width=480)
#dev.off() 

´´´